---
title: "pe-STARR-Seq"
author: "Vincent Loubiere"
date: '2022-10-14'
output:                                                                    
  html_document:                                                           
    toc: true                                                              
    number_sections: true                                                  
    code_folding: "hide"                                                   
    toc_float:                                                             
      collapse: false                                                      
      smooth_scroll: false
    css: styles.css
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width = "1250px", out.height = "625px")
```

# Figure 1
## Main
### pe-STARR-Seq sketch
```{r}
knitr::include_graphics("../pdf/draft/Sketch_peSTARRSeq.pdf")
```
### PCC left right activities
```{r}
knitr::include_graphics("../pdf/draft/Correlation_left_rigth_activities.pdf")
```
### Single enhancer vs pairs
```{r}
knitr::include_graphics("../pdf/draft/Compare_individual_vs_enh_pairs.pdf")
```
## Supplementary
### PCC replicates
```{r}
knitr::include_graphics("../pdf/draft/PCC_peSTARRSeq_replicates_vllib002.pdf")
```
### Candidates classification act/inact
```{r}
knitr::include_graphics("../pdf/draft/Candidates_classification_vllib002.pdf")
```
### PCC luciferase validations
```{r}
knitr::include_graphics("../pdf/draft/Luciferase_validations.pdf")
```

# Figure 2
## Main
### Compare additive multiplicative model
```{r}
knitr::include_graphics("../pdf/draft/Compare_add_mult_vllib002.pdf")
```
### Linear model
```{r}
knitr::include_graphics("../pdf/draft/CV_linear_model_vllib002.pdf")
```
### Ordered residuals heatmap
```{r}
knitr::include_graphics("../pdf/draft/heatmap_ordered_ind_act.pdf")
```
### Individual act vs synergy
```{r}
knitr::include_graphics("../pdf/draft/individual_strengths_vs_synergy.pdf")
```
## Supplementary
### CP staturation
```{r}
knitr::include_graphics("../pdf/draft/promoter_saturation.pdf")
```
### UMI staturation
```{r}
knitr::include_graphics("../pdf/draft/umi_saturation.pdf")
```

# Figure 3
## Main
### Example pairs similar act. but different residuals
```{r}
knitr::include_graphics("../pdf/draft/lm_residuals_examples_vllib002.pdf")
```
### Density residuals, symmetry and motif enrichment
```{r}
knitr::include_graphics("../pdf/draft/density_residuals_motif_enrichment_vllib002.pdf")
```
### Heatmap motif contribution residuals
```{r}
knitr::include_graphics("../pdf/draft/heatmap_motif_residuals_prediction.pdf")
```

# Figure 4
## Main
### Compare DSCP/RpS12
```{r}
knitr::include_graphics("../pdf/draft/Compare_add_mult_vllib15_16_residuals.pdf")
```

